NEED A BETTER TITLE: A co-moving pair of bright stars \\ with very different metallicities and abundances

### 2017-04-13 paper/ms.tex
words on peculiarity of HD30

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb}
\usepackage{tikz}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}

@@

The abundance of HD 30 is peculiar on its own compared to other disk stars with
similar $[\elem{Fe}/\elem{H}]$. \todo{discuss}

@@

>>>>

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb,natbib}
\usepackage{tikz}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}

@@

The abundance of HD 30 is peculiar on its own compared to other disk stars with
similar $[\elem{Fe}/\elem{H}]$.
For a star with $[\elem{Fe}/\elem{H}] \approx 0.2$, we generally expect
$[\elem{Na}/\elem{Fe}] > 0$ and $[\elem{Mn}/\elem{Fe}] > -0.1$
(\citealt{Battistini:2015aa,Bensby:2003aa}) making the abundances of HD 30 ever more unlikely.
We stress that none of the binary pairs examined in \citealt{2016ApJS..225...32B}
show discrepancies in abundances between the stars at this level.
In fact, no strong trend is found in pair for most elements
except N and Y.
For Y, the trend for this pair is opposite of the others in Teff.
Specifically, no difference within pair is found for Mn.

@@

None of the above scenarios is quite satisfactory as it offers no
insight on the peculiarity in abundances of HD 30 (see \ref{sec:data}).
